Global patterns of forest autotrophic carbon fluxes

### 2020-12-17 manuscript/manuscript draft.Rmd
updated table

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypothesis_table[1,1] <- paste0(hypothesis_table[1,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(2),"$^{,}$", footnote_marker_number(3)) #Luyssaert, Gillman et al. (2015)", "Simova and Storch (2017)"
hypothesis_table[2,1] <- paste0(hypothesis_table[2,1], footnote_marker_number(1),"$^{,}$", footnote_marker_number(10)) #Luyssaert, Huston & Wolverton
hypothesis_table[3,1] <- paste0(hypothesis_table[3,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4),"$^{,}$",footnote_marker_number(9)) ## Luyssaert, Schuur, Piao, Wei
hypothesis_table[4,1] <- paste0(hypothesis_table[4,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4)) ## Luyssaert, Schuur, Wei
hypothesis_table[5,1] <- paste0(hypothesis_table[5,1], footnote_marker_number(5)) ### Taylor, muller Landau
hypothesis_table[8,1] <- paste0(hypothesis_table[8,1], footnote_marker_number()) ### fyllas
hypothesis_table[11,1] <- paste0(hypothesis_table[11,1], footnote_marker_number(6),"$^{,}$",footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
hypothesis_table[12,1] <- paste0(hypothesis_table[12,1], footnote_marker_number(7),"$^{,}$", footnote_marker_number(8))
hypothesis_table[13,1] <- paste0(hypothesis_table[13,1], footnote_marker_number(8))
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Summary of review questions, corresponding expectations based on previous studies (when applicable), and results. Statistically signficant support for/ rejection of hypotheses is indicated by checkmarks/ X's, and '-' indicates no significant relationship. Parentheses indicate partial overall support or rejection of hypotheses across all fluxes considered. Flux variables are defined in Table 2.", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do C fluxes vary with latitude?", 1, 2,  colnum =7, hline_before = FALSE) %>%
  pack_rows("Q2. How do C fluxes vary with mean annual temperature (MAT) and precipitation (MAP)?", 3, 5,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q3. How are C fluxes related to other annual climate variables?", 6, 8,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence annual C fluxes?", 9, 12,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do annual C fluxes still vary with climate?", 13, 16, colnum = 7, hline_before = TRUE) %>%
  add_header_above(c(" ",  " ", "Forest autotrophic carbon fluxes" = 9, " ")) %>%
  #column_spec(2:11, width = "1.8cm") %>%
  kableExtra::landscape() 
  #kableExtra::footnote(number = c("Luyssaert et al. (2007)", "Gillman et al. (2015)", "Simova and Storch (2017)", "Schuur (2003)", "Taylor et al. (2017)", "Malhi (2012)", "Michaletz et al. (2014)", "Chu et al. (2016)", "Piao et al. (2010)", "Huston & Wolverton (2009)", "Wei et al. (2010)), footnote_as_chunk = TRUE)
```

>>>>

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypothesis_table[1,1] <- paste0(hypothesis_table[1,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(2),"$^{,}$", footnote_marker_number(3)) #Luyssaert, Gillman et al. (2015)", "Simova and Storch (2017)"
hypothesis_table[2,1] <- paste0(hypothesis_table[2,1], footnote_marker_number(1),"$^{,}$", footnote_marker_number(4)) #Luyssaert, Huston & Wolverton
hypothesis_table[3,1] <- paste0(hypothesis_table[3,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(5),"$^{,}$",footnote_marker_number(6),"$^{,}$",footnote_marker_number(7)) ## Luyssaert, Schuur, Piao, Wei
hypothesis_table[4,1] <- paste0(hypothesis_table[4,1], footnote_marker_number(1),"$^{,}$",footnote_marker_number(4),"$^{,}$",footnote_marker_number(7)) ## Luyssaert, Schuur, Wei
hypothesis_table[5,1] <- paste0(hypothesis_table[5,1], footnote_marker_number(8),"$^{,}$",footnote_marker_number(9)) ### Taylor, muller Landau
hypothesis_table[8,1] <- paste0(hypothesis_table[8,1], footnote_marker_number(10),"$^{,}$",footnote_marker_number(11)) ### fyllas nemani
hypothesis_table[10,1] <- paste0(hypothesis_table[10,1], footnote_marker_number(12),"$^{,}$",footnote_marker_number(13)) ## wagner 2016 + 2014
hypothesis_table[11,1] <- paste0(hypothesis_table[11,1], footnote_marker_number(14),"$^{,}$",footnote_marker_number(15),"$^{,}$", footnote_marker_number(16))
hypothesis_table[12,1] <- paste0(hypothesis_table[12,1], footnote_marker_number(15),"$^{,}$", footnote_marker_number(16))
hypothesis_table[13,1] <- paste0(hypothesis_table[13,1], footnote_marker_number(16))
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Summary of review questions, corresponding expectations based on previous studies (when applicable), and results. Statistically signficant support for/ rejection of hypotheses is indicated by checkmarks/ X's, and '-' indicates no significant relationship. Parentheses indicate partial overall support or rejection of hypotheses across all fluxes considered. Flux variables are defined in Table 2.", escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("Q1. How do C fluxes vary with latitude?", 1, 2,  colnum =7, hline_before = FALSE) %>%
  pack_rows("Q2. How do C fluxes vary with mean annual temperature (MAT) and precipitation (MAP)?", 3, 5,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q3. How are C fluxes related to other annual climate variables?", 6, 8,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q4. How does seasonality influence annual C fluxes?", 9, 12,  colnum = 7, hline_before = TRUE) %>%
  pack_rows("Q5. When standardised by growing season length, how do annual C fluxes still vary with climate?", 13, 16, colnum = 7, hline_before = TRUE) %>%
  add_header_above(c(" ",  " ", "Forest autotrophic carbon fluxes" = 9, " ")) %>%
  #column_spec(2:11, width = "1.8cm") %>%
  kableExtra::landscape() %>%
  kableExtra::footnote(number = c("Luyssaert et al. (2007)", "Gillman et al. (2015)", "Simova and Storch (2017)", "Huston & Wolverton (2009)", "Schuur (2003)", "Piao et al. (2010)", "Wei et al. (2010)", "Taylor et al. (2017)", "Muller-Landau et al. (2020)", "Fyllas et al. (2017)", "Nemani et al. (2003)", "Wagner et al. (2014)" , "Wagner et al. (2016)", "Malhi (2012)", "Michaletz et al. (2014)", "Chu et al. (2016)"), footnote_as_chunk = TRUE)
```
